### 2017-11-06 Draft2/FieldsProperties.tex
More stuff for today
Modify the ctors
Wording

As a dynamic array, $\VarList$ is also given the following properties. $:=$ denotes a definition, as opposed to $=$ which checks equivalence. Functions that return boolean values are suffixed with ?.

@@

\begin{algorithm}
	\begin{algorithmic}
		\Procedure{$\FuncConstructor$}{$\VarList$}
			\State $\VarList.\FieldBuffer \gets \FuncNewArray(0)$
			\State $\VarList.\FieldSize \gets 0$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

\begin{itemize}
	\item $\VarList.\FieldHead$ - The \textbf{head} of $\VarList$. It returns the buffer we are currently adding items to.
	\item $\VarList.\FieldTail$ - The \textbf{tail} of $\VarList$. \textbf{Important note: The tail is a dynamic array.} It returns a \textit{dynamic array} of references to buffers that are already filled with items. The tail can be thought of as a two-dimensional array.\\
	{\HdrNote} It may seem strange for a growth array to use the very data structure it is replacing. As shown in Lemma \ref{lem:VarUsefulIsOLogN}, however, only $O(\log n)$ many references are appended to the tail. Thus, the extra copying and allocations the tail performs is minuscule compared to other work done by the growth array.
	\item $\VarList.\FieldSize$ - The number of items in $\VarList$.
	\item $\VarList.\FieldCapacity$ - The \textbf{capacity} of $\VarList$. It returns the maximum number of items $\VarList$ can hold without resizing.
\end{itemize}

@@

\begin{algorithm}
	\begin{algorithmic}
		\Procedure{$\FuncConstructor$}{$\VarList$}
			\State $\VarList.\FieldHead \gets \FuncNewArray(0)$
			\State $\VarList.\FieldTail \gets \FuncNewDynamicArray()$
			\State $\VarList.\FieldSize \gets 0$
			\State $\VarList.\FieldCapacity \gets 0$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

>>>>

As a dynamic array, $\VarList$ is also given the following properties. {\HdrNote} For pseudocode, I will use $:=$ to denote a definition, and $=$ to denote an equivalence check. Functions that return boolean values are suffixed with ?.

@@

\begin{algorithm}
	\begin{algorithmic}
		\Procedure{$\FuncConstructor$}{$\VarList$}
			\State $\VarList.\FieldBuffer \gets \FuncNewArray(\VarInitCapacity)$
			\State $\VarList.\FieldSize \gets 0$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

\begin{itemize}
	\item $\VarList.\FieldHead$ - The \textbf{head} of $\VarList$. It returns the buffer we are currently adding items to.
	\item $\VarList.\FieldTail$ - The \textbf{tail} of $\VarList$. \textbf{Important note: The tail is a dynamic array.} It returns a \textit{dynamic array} of references to buffers that are already filled with items. The tail can be thought of as a two-dimensional array.\\
	{\HdrNote} It may seem strange for a growth array to use the very data structure it is replacing. As shown in Lemma \ref{lem:VarUsefulIsOLogN}, however, only $O(\log n)$ many references are appended to the tail. Thus, the extra copying and allocations the tail performs is minuscule compared to other work done by the growth array.
	\item $\VarList.\FieldSize$ - The number of items in $\VarList$.
	\item $\VarList.\FieldCapacity$ - The \textbf{capacity} of $\VarList$. It returns the maximum number of items $\VarList$ can hold before it must grow.
\end{itemize}

@@

\begin{algorithm}
	\begin{algorithmic}
		\Procedure{$\FuncConstructor$}{$\VarList$}
			\State $\VarList.\FieldHead \gets \FuncNewArray(\VarInitCapacity)$
			\State $\VarList.\FieldTail \gets \FuncNewDynamicArray()$
			\State $\VarList.\FieldSize \gets 0$
			\State $\VarList.\FieldCapacity \gets \VarInitCapacity$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}
